Gafo-cc data processing

### 2023-12-11 analysis/gafo-cc-data-processing.Rmd
add model data

```{r}
tidy_data_nz%>%
  filter(trialType == "test")%>%
  group_by(subjID)%>%
  summarise(n = n())

@@

data_nz%>%
  group_by(age)%>%
  summarise(n())
```

@@

@@

@@

```{r}
data_tur <- tidy_demographics_tur%>%
  left_join(tidy_data_tur%>%rename_all(tolower),by = c("subjid"))%>%
  mutate(community = "turkey")%>%
  distinct(subjid, trialnr, .keep_all = TRUE)%>%
  mutate(subjid = recode(subjid, 
                     "EBRAR100" = "TUR00002",
                     "FATMA400" = "TUR00003",
                     "ASYAA200" = "TUR00004"))

@@

data_tur%>%
  group_by(subjid)%>%
  summarise(n = n(), 
            mean = mean(abs(clickdistfromtargetcenterx)))

@@

# Merge
```{r}
merge_raw_data <- bind_rows(
  data_zambia,
  data_namibia%>%rename(younger_children = youngerchildren),
  data_leipzig,
  data_nigeria,
  data_plymouth,
  data_stanford,
  data_mex,
  data_china, 
  data_arg,
  data_ind,
  data_nz
)%>%
  #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
  filter(trialtype == "test",
         voiceover == F
         )%>%
  mutate(age_group = substr(ageinyears, 1,1), 
         trialnr = as.numeric(factor(trialnr)))

@@

@@

```{r}
merge_raw_data <- read_csv("../data/gafo-cc-raw-data.csv")
```

```{r}
chimfunshi_data <- merge_raw_data%>%
  filter(community == "chimfunshi",
         voiceover == F)%>%
  mutate(agecentered = ageinyears - min(ageinyears))%>%
  select(-c(sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site,`location` ))

write(toJSON(chimfunshi_data), file = "../model/model_data/chimfunshi-model-data.json")
```

```{r}
haillom_data <- merge_raw_data%>%
  filter(community == "hai||om",
         voiceover == F)%>%
  mutate(agecentered = ageinyears - min(ageinyears))%>%
  select(-c(sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site,`location` ))

write(toJSON(haillom_data), file = "../model/model_data/haillom-model-data.json")

write_csv(mdata, file = "../model/model_data/gafo-cc-model-data.csv")
```

>>>>

```{r}
tidy_data_nz%>%
  #filter(trialType == "test")%>%
  group_by(subjID)%>%
  summarise(n = n())

@@

# data_nz%>%
#   group_by(age)%>%
#   summarise(n())
```

@@

    datacollection = as.factor("in-person - supervised"), 
    sample = as.factor("na"),
    studytype = as.factor("vali"),
    subjID = as.character(subjID),
    subjID = ifelse(subjID == "TUR79000", "TUR00079",subjID),
    subjID = ifelse(subjID == "TUR80000", "TUR00080",subjID),
    subjID = ifelse(subjID == "TUR81000", "TUR00081",subjID),
    subjID = ifelse(subjID == "TUR83000", "TUR00083",subjID),
    subjID = ifelse(subjID == "TUR84000", "TUR00084",subjID),
    subjID = ifelse(subjID == "TUR85000", "TUR00085",subjID)
  ) %>%select(-touchScreen)%>%
  mutate(subjID = factor(subjID))#%>%select(subjID, population, trialType, trialNr, targetPosition, targetCentralityX, clickDistFromTargetCenterX)
```

@@

unique(tidy_data_tur$subjID)
```

@@

```{r}
data_tur <- tidy_demographics_tur%>%
  left_join(tidy_data_tur%>%rename_all(tolower),by = c("subjid"))%>%
  mutate(community = "turkey")%>%
  distinct(subjid, trialnr, .keep_all = TRUE)%>%
  mutate(subjid = recode(subjid, 
                     "EBRAR100" = "TUR00001",
                     "FATMA400" = "TUR00002",
                     "ASYAA200" = "TUR00003"))

@@

data_tur%>%
  mutate(age_group = substr(ageinyears, 1,1))%>%
  group_by(age_group)%>%
  summarise(n = n_distinct(subjid))

@@

# Congo

```{r read_data}
# get all .json files
files <- list.files("../../../../../../Cloud/QuantEx/Gafo-cc/data/congo/data_GaFo/", pattern = "*.json",recursive = T)

# convert json files to tibbles
raw_data_cong <- tibble()
for (f in files) {
  jf <- paste("../../../../../../Cloud/QuantEx/Gafo-cc/data/congo/data_GaFo/", f, sep = "")
  jd <- jsonlite::fromJSON(paste(readLines(jf, warn = "FALSE"), collapse = ""))

  raw_data_cong <- bind_rows(raw_data_cong, jd)
}
# remove variables that we don't need anymore
rm(f, files, jf, jd)
```

```{r}
tidy_data_cong <- raw_data_cong %>%

```{r}
tidy_data_cong%>%
  summarise(n = n_distinct(subjID))

tidy_data_cong%>%
  group_by(subjID)%>%
  summarise(n = n())

```{r }
raw_demographics_cong <- bind_rows(
    read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/congo/gafo-cc-congo-participants_2023_V3.xlsx", sheet = 1)%>%
      mutate(household = as.character(household),
             children = as.character(children),
             younger_children = as.character(younger_children)),
    read_xlsx("../../../../../../Cloud/QuantEx/Gafo-cc/data/congo/gafo-cc-congo-participants_2023_V3.xlsx", sheet = 2),
  )

tidy_demographics_cong <- raw_demographics_cong %>%
  filter(birth_date != "NA")%>%
  filter(status == "keep", id != "BD000001", id != "BY000001")%>%
  mutate(
    test_date = as.Date(as.character(test_date), format = "%Y%m%d"),
    birth_date = as.Date(as.character(birth_date), format = "%Y%m%d"),
    ageinyears = as.numeric(difftime(test_date,birth_date, units = "days")/365.25),
    screen = ifelse(screen == "fallaci", 0, 1), 
    touchscreen = ifelse(touchscreen == "fallaci", 0, 1),
    household = as.numeric(household), 
    children = as.numeric(children),
    younger_children = as.numeric(younger_children)
  )  %>%
  select(-c(first_name, last_name, test_date, birth_date, comment))%>%
  #filter(!is.na(ageinyears))%>%
  rename(subjid = id)

```{r}
data_cong <- tidy_demographics_cong%>%
  left_join(tidy_data_cong%>%rename_all(tolower),by = c("subjid"))%>%
  #mutate(community = "congo")%>%
  distinct(subjid, trialnr, .keep_all = TRUE)

data_cong%>%
  group_by(subjid)%>%
  summarise(n = n())

data_cong%>%
  group_by(subjid)%>%
  summarise(n = n(), 
            mean = mean(abs(clickdistfromtargetcenterx)))

```
# Merge
```{r}
merge_raw_data <- bind_rows(
  data_zambia,
  data_namibia%>%rename(younger_children = youngerchildren),
  data_leipzig,
  data_nigeria,
  data_plymouth,
  data_stanford,
  data_mex,
  data_china, 
  data_arg,
  data_ind,
  data_nz, 
  data_tur,
  data_cong
)%>%
  #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
  filter(trialtype == "test",
         voiceover == F
         )%>%
  mutate(age_group = substr(ageinyears, 1,1), 
         trialnr = as.numeric(factor(trialnr)))

@@

methods_data <- merge_raw_data%>%
  select(subjid, community, age_group, ageinyears, trialnr, targetposition,targetcentralityx, clickdistfromtargetcenterx)%>%
  filter(ageinyears > 1)

write_csv(methods_data,"../../tango-cc-methods/data/data.csv")
```

```{r}
fam_excl <- bind_rows(
  data_zambia,
  data_namibia%>%rename(younger_children = youngerchildren),
  data_leipzig,
  data_nigeria,
  data_plymouth,
  data_stanford,
  data_mex,
  data_china, 
  data_arg,
  data_ind,
  data_nz, 
  data_tur,
  data_cong
)%>%
  filter(trialtype != "test")%>%
  group_by(subjid,community)%>%
  mutate(click = abs(clickdistfromtargetcenterx))%>%
  summarise(mean_click = mean(click))%>%
  filter(mean_click > 100)%>%
  pull(subjid)
```

@@

```{r}

communities <- unique(merge_raw_data$community)

for (i in communities) {

m_data <- merge_raw_data%>%
  filter(community == i,
         voiceover == F)%>%
  mutate(agecentered = ageinyears - min(ageinyears))%>%
  select(-c(sex,ageinyears, wrongareaclick, earlyclick, durationanimationballoontotal, durationanimationcomplete, responsetime, clientscreenwidth, clientscreenheight, clientscreenscaling, clickoriginalx, clickoriginaly, hitbbtargetx, hitbbtargety, clickdistfromtargetbboxx, clickedarea, studyversion, boxesnr,population, inhouse, os, mobile, browser, browserversion, safari, iossafari,target, voiceover, epoch, timestamp, inwardclick, boxwidth,boxborderleft, boxborderright , correctbox, datacollection, sample, studytype, comment, status, site,`location` ))

write(toJSON(m_data), file = paste0("../model/model_data/", i, "-model-data.json"))

#write_csv(mdata, file = "../model/model_data/", i, "-model-data.csv")

}
